---
title: "P8105 HW 1"
author: "Yiying Chen yc4776"
date: "2025-09-19"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
library(moderndive) #call the function for problem 1

library(tidyverse) #call the function for ggplot in problem1 and data frame in problem2
```
## Problem1
```{r problem_1_data_import}

data("early_january_weather")

```

#Key variables include time_hour, temperature and humidity.  
#For time_hour, the key value is that <br/>`r paste(capture.output(summary(early_january_weather$time_hour)),collapse = "<br>")`.  
#For temperature, the key value is that <br/>`r paste(capture.output(summary(early_january_weather$temp)),collapse = "<br>")`.  
#For humidity, the key value is that <br/>`r paste(capture.output(summary(early_january_weather$humid)),collapse = "<br>")`.  
#All variables are: `r names(early_january_weather)`.  
#This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
#The mean temperature is `r mean(early_january_weather$temp)` °F.  

```{r problem_1_plot}

#make ggplot of temperature v.s. time_hour
temp_time_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp)) + 
  geom_point(aes(color = humid), alpha = .5) +
  labs(
    title = "Temperature vs Time in Early January",
    subtitle = "Color = Humidity",
    x = "Time",
    y = "Temperature")

temp_time_plot

ggsave("p8105_HW1_plot.png", temp_time_plot, width = 8, height = 5)

```
#Even though the plot is fluctuating, the general pattern is showing an upward trend, with a peak around Jan 14–15.  

